A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-09 4_method.tex
make figure positions floating

\paragraph{line-line bones}
When the angle between two outline segments is small, the naive method will produce long triangular gaps.
A computationally efficient way to compute $\alpha$ can be obtained by looking at the ratio between $R$ and Euclidean distance.
Equivalently we can compare the Euclidean distance between two vertices with the difference in distance measure;
if $ |v_1 - v_0| > 2 | R(v_1) - R(v_0) |$ then $\alpha > \SI{120}{\degree}$.

\begin{figure}[H]
\centering
\includegraphics[width=.9\columnwidth]{sources/method/distance_based_angles.pdf}
\caption{Distance based angle estimation. By comparing the euclidean distance between two vertices with the distance measure of the MAT we can skip comparing the angles between the outline segments.}
\label{distance_based_angles}
\end{figure}

The Euclidean distance between two MAT vertices can never be less than the difference in the MAT distance measure between the vertices:t
\begin{figure}[H]
\centering
\includegraphics[width=.3\columnwidth]{sources/method/distance_ratio_limit.pdf}
\caption{Minimal Euclidean distance for a given difference in MAT distance measure.}
\label{distance_ratio_limit}
\end{figure}

\paragraph{line-point segments}
For a parabola MAT segment generated by point $(0,d)$ and an outline segment lying on the x-axis, the parabola is given by $y = \frac{1}{2d} x^2 + \frac12 d$.
If $\alpha > \SI{120}{\degree}$ then $\tan^{-1} \abs \partial y / \partial x < \SI{30}{\degree}$,
i.e.  $\tan^{-1} \abs x/d < \SI{30}{\degree}$,
i.e. when $\abs x/d < 1 / \sqrt{3}$,
i.e. when $\abs x < d \sqrt{3} / 3$.
So we mark the part of the parabola as to-be-transformed for which $x \in [-d \sqrt{3} / 3, d \sqrt{3} / 3]$.

\begin{figure}[H]
\centering
\includegraphics[width=.5\columnwidth]{sources/method/end_of_markings_point_line.pdf}
\caption{End-of-markings for a parabolic spine segment.}
\label{end_of_markings_point_point}
\end{figure}

\paragraph{point-point bones}
For a segment gerenated by points $(0,0)$ and $(0,d)$, the angle $\alpha > \SI{120}{\degree}$ when $\abs(x) < \frac12 d \tan \SI{30}{\degree} $,
so we mark the part of the straight MAT segment as to-be-transformed for which $x \in [-d \sqrt{3}/6, d \sqrt{3}/6]$.

\begin{figure}[H]
\centering
\includegraphics[width=.3\columnwidth]{sources/method/end_of_markings_point_point.pdf}
\caption{End-of-markings for the segment(s) generated by two outline verts.}
\label{end_of_markings_point_point}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=.75\columnwidth]{sources/method/transition_length_v2.pdf}
\caption{Transition length on a line-line segment.}
\label{transition_length}
\end{figure}

The position of a transition should be at a location $p$ where $\exists n : R(p) = b^{-1}(n)$.
However, given the fact that a transition is a region rather than a point, which part of the transition should be ceneterd at $p$?
For a transition from $n$ to $n+\frac12$ beads, we place a fraction of the transition length toward the end with lower $R$ proportional to it's positioning within the region of non-prefered widths:
$ (b^{-1}(n+\frac12) - p(n) ) / (p(n + \frac12) - p(n))$

\begin{figure}[H]
\centering
\includegraphics[width=.5\columnwidth]{sources/method/transition_location_precise.pdf}
\caption{Transition placement. The anchor position within the transition length is proportional to the transition location within the range between two distances with prefered length. \hl{outdated functions and variables!}}
\label{transition_length}
\end{figure}

@@

\begin{figure}[H]
\centering
\includegraphics[width=.9\columnwidth]{sources/method/distance_rounding_transition.pdf}
\caption{MAT distance remapping.}
\label{distance_rounding_transition}
\end{figure}

@@

\begin{figure}[H]
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/change_to_marked.pdf}
\caption{before end of markings}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/change_to_marked_2.pdf}
\caption{after end of markings}
\end{subfigure}
\caption{Transition near end of markings. The gap depends on the positioning of the middle of the transition (dotted lines) with respect to the end of the marked areas.}
\label{change_to_marked}
\end{figure}

>>>>

\paragraph{line-line bones}
When the angle between two outline segments is small, the naive method will produce long triangular gaps.
A computationally efficient way to compute $\alpha$ can be obtained by looking at the ratio between $R$ and Euclidean distance.
Equivalently we can compare the Euclidean distance between two vertices with the difference in distance measure;
if $ |v_1 - v_0| > 2 | R(v_1) - R(v_0) |$ then $\alpha > \SI{120}{\degree}$.
See \cref{distance_based_angles}.

\begin{figure}
\centering
\includegraphics[width=.9\columnwidth]{sources/method/distance_based_angles.pdf}
\caption{Distance based angle estimation. By comparing the euclidean distance between two vertices with the distance measure of the MAT we can skip comparing the angles between the outline segments.}
\label{distance_based_angles}
\end{figure}

The Euclidean distance between two MAT vertices can never be less than the difference in the MAT distance measure between the vertices: \cref{distance_ratio_limit}.

\begin{figure}
\centering
\includegraphics[width=.3\columnwidth]{sources/method/distance_ratio_limit.pdf}
\caption{Minimal Euclidean distance for a given difference in MAT distance measure.}
\label{distance_ratio_limit}
\end{figure}

\paragraph{line-point segments}
For a parabola MAT segment generated by point $(0,d)$ and an outline segment lying on the x-axis, the parabola is given by $y = \frac{1}{2d} x^2 + \frac12 d$.
If $\alpha > \SI{120}{\degree}$ then $\tan^{-1} \abs \partial y / \partial x < \SI{30}{\degree}$,
i.e.  $\tan^{-1} \abs x/d < \SI{30}{\degree}$,
i.e. when $\abs x/d < 1 / \sqrt{3}$,
i.e. when $\abs x < d \sqrt{3} / 3$.
So we mark the part of the parabola as to-be-transformed for which $x \in [-d \sqrt{3} / 3, d \sqrt{3} / 3]$.
See \cref{end_of_markings_point_point}.

\begin{figure}
\centering
\includegraphics[width=.5\columnwidth]{sources/method/end_of_markings_point_line.pdf}
\caption{End-of-markings for a parabolic spine segment.}
\label{end_of_markings_point_point}
\end{figure}

\paragraph{point-point bones}
For a segment gerenated by points $(0,0)$ and $(0,d)$, the angle $\alpha > \SI{120}{\degree}$ when $\abs(x) < \frac12 d \tan \SI{30}{\degree} $,
so we mark the part of the straight MAT segment as to-be-transformed for which $x \in [-d \sqrt{3}/6, d \sqrt{3}/6]$.
See \cref{end_of_markings_point_point}.

\begin{figure}
\centering
\includegraphics[width=.3\columnwidth]{sources/method/end_of_markings_point_point.pdf}
\caption{End-of-markings for the segment(s) generated by two outline verts.}
\label{end_of_markings_point_point}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=.75\columnwidth]{sources/method/transition_length_v2.pdf}
\caption{Transition length on a line-line segment.}
\label{transition_length}
\end{figure}

The position of a transition should be at a location $p$ where $\exists n : R(p) = b^{-1}(n)$.
However, given the fact that a transition is a region rather than a point, which part of the transition should be ceneterd at $p$?
For a transition from $n$ to $n+\frac12$ beads, we place a fraction of the transition length toward the end with lower $R$ proportional to it's positioning within the region of non-prefered widths:
$ (b^{-1}(n+\frac12) - p(n) ) / (p(n + \frac12) - p(n))$
See \cref{transition_placement}.

\begin{figure}
\centering
\includegraphics[width=.5\columnwidth]{sources/method/transition_location_precise.pdf}
\caption{Transition placement. The anchor position within the transition length is proportional to the transition location within the range between two distances with prefered length. \hl{outdated functions and variables!}}
\label{transition_placement}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=.9\columnwidth]{sources/method/distance_rounding_transition.pdf}
\caption{MAT distance remapping.}
\label{distance_rounding_transition}
\end{figure}

@@

\begin{figure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/change_to_marked.pdf}
\caption{before end of markings}
\end{subfigure}
\begin{subfigure}{0.45\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/change_to_marked_2.pdf}
\caption{after end of markings}
\end{subfigure}
\caption{Transition near end of markings. The gap depends on the positioning of the middle of the transition (dotted lines) with respect to the end of the marked areas.}
\label{change_to_marked}
\end{figure}
